---
title: "HW5"
output: pdf_document
---

# HW5

All students will receive full credit for questions 1, 2, and 3

### 1. 1 point

What has been your favorite part of this class?

### 2. 1 point

What has been your least favorite part of this class?

### 3. 1 point

What could be changed to create a better learning environment?


### 4. (ROS 4.3) 2 points
_Comparison of proportions:_ You want to gather data to determine which of two students is a better basketball shooter. One of them shoots with 30% accuracy and the other is a 40% shooter. Each student takes 20 shots and you then compare their shooting percentages. What is the probability that the better shooter makes more shots in this small experiment?

### 5. (based on ROS 4.4) 5 points
_Designing an experiment:_ Now, you want to gather data to determine which of the two students is a better basketball shooter. Assume student one has 30% accuracy and student 2 has 40% accuracy. The goal is to choose N, the number of shots taken, so that you have a good chance to identify the better shooter. Your collaborator, the head basketball coach, says they have time for each student to take up to 200 shots. Create a graphic that shows the probability that better shooter makes more shots as a function of N (Consider starting with 20 shots and going to 40, 60,80,100,120,140,160,180,200).

### 6.

#### a. (4 points)
Run the code below and describe the data simulation process and the expected results (minimum p-value) for model 1 and model 2.

```{r}
# initialize
set.seed(09102020)
num_replications <- 100
num_obs <- 50
num_preds <- 10

# simulate model 1 data
X <- matrix(rnorm(num_preds * num_obs), num_obs, num_preds)
y <- rnorm(num_obs)

# fit and summarize model 1
lm1 <- lm(y ~ X)
summary(lm1)
min_pvalue1<- min(summary(lm1)$coefficients[,4])

# simulate model 2 data
X <- matrix(rnorm(num_preds * num_obs), num_obs, num_preds)
y <- X[,1] + rnorm(num_obs)

#fit and summarize model 2
lm2 <- lm(y ~ X)
summary(lm2)
min_pvalue2 <- min(summary(lm2)$coefficients[,4])
```

#### b. (4 points)
Now run the code below which loops through part a 100 times. Summarize your findings for the minimum p-values for each model. What proportion of the time is there a _significant_ result for each model?

```{r}
#intialize
set.seed(09102020)
min_pvalue <- matrix(0, num_replications, 2)

for (rep in 1:num_replications){
  # fit model 1 and store min p-value
  X <- matrix(rnorm(num_preds * num_obs), num_obs, num_preds)
  y <- rnorm(num_obs)
  lm1 <- lm(y ~ X)
  min_pvalue[rep,1] <- min(summary(lm1)$coefficients[,4])
  
  # fit model 2 and store min p-value
  X <- matrix(rnorm(num_preds * num_obs), num_obs, num_preds)
  y <- X[,1] + rnorm(num_obs)
  lm2 <- lm(y ~ X)
  min_pvalue[rep,2] <- min(summary(lm2)$coefficients[,4])
}
```
